Generating the Blueprints of the Maven Repository

### 2015-01-25 msr.tex
added title

\title{The Three Corridors}

@@

\begin{itemize}
  \item \textbf{CKJM-ext} \textit{(ckjm)}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}.

  \item \textbf{JDepend} \textit{(jdep)}

  \item \textbf{CLMT} \textit{(clmt)}
\end{itemize}

@@

>>>>

\title{Generating the Blueprints of the Maven Repository}

@@

@@

\section{The Toolset}

Three tools were selected.

\begin{itemize}
  \item \textbf{CKJM-ext} \textit{(ckjm)}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}. The version of the tool that we used for this experinment can be found in github\footnote{\url{https://github.com/bkarak/ckjm_ext}}.

  \item \textbf{JDepend} \textit{(jdep)}\footnote{\url{http://clarkware.com/software/JDepend.html}} is an source tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.

  \item \textbf{CLMT} \textit{(clmt)} stands for cross-language metric tool and analyses Java source code in order to calculate a series of metrics.
\end{itemize}

Table~\ref{tbl:selected-metrics} presents the key metrics that exist in the dataset. Note that each tool
